Calculate FD

### 2020-07-02 analysis/calc_fd.Rmd
work around the potential empty dataframes

  future::plan(multiprocess)
  fd <- future_map_dfr(group_plots$plot_id, get_fd_safe, data = group_data)

@@

fd <- map_dfr(1:num_groups, get_parallel_FD, data = data)
```

@@

remain <- biotime_traits %>%
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  filter(!is.na(plot), !study_id %in% c(195, 360),
         !study_id %in% c(217, 327), #exclude to get the file size smaller
         !study_id %in% c(59, 166, 337), #NA's in the distance matrix
         study_id != 169,  #Zero distance error
         !study_id %in% c(372,374), #Qhull error code 4
         study_id != 333) %>% #species distance matrix not Euclidean after 'sqrt' correction
  filter(study_id != 56 | plot != 24) %>% #NA's in the distance matrix
  anti_join(fd_data, by = c("year", "study_id", "plot")) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup()

plots <- remain %>%
  pull(plot_id) %>%
  unique()

>>>>

  future::plan(multiprocess)
  fd <- future_map(group_plots$plot_id, get_fd_safe, data = group_data) %>%
    rbind()

@@

fd <- map(1:num_groups, get_parallel_FD, data = data)
```

@@

# remain <- data %>%
#   filter(!is.na(plot)) %>% #remove unlabeled plots 
#   filter(!is.na(plot), !study_id %in% c(195, 360),
#          !study_id %in% c(217, 327), #exclude to get the file size smaller
#          !study_id %in% c(59, 166, 337), #NA's in the distance matrix
#          study_id != 169,  #Zero distance error
#          !study_id %in% c(372,374), #Qhull error code 4
#          study_id != 333) %>% #species distance matrix not Euclidean after 'sqrt' correction
#   filter(study_id != 56 | plot != 24) %>% #NA's in the distance matrix
#   anti_join(fd_data, by = c("year", "study_id", "plot")) %>%
#   group_by(study_id, year, plot) %>%
#   filter(n_distinct(id) > 4) %>%
#   ungroup()

plots_left <- plots[!plots %in% fd_data$plot_id]

library(furrr)
future::plan(multiprocess)
system.time(fd <- future_map(plots_left, get_fd_safe, data = data))
```
